Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-22 ms.tex
I updated the Mie scattering figure with a MCMC model fit.

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.  {\bf [PHASE VARIATION]}. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths. An alternate model based on surface hot spots requires implausibly large temperature variations. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption. The data are fit] with simple Mie scattering models with a log-normal particle size distribution of forsterite grains.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

>>>>

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.  {\bf [PHASE VARIATION]}. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths. An alternate model based on surface hot spots requires implausibly large temperature variations. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}
